The Driving Forces of API Evolution

### 2015-06-02 thesis/paper.tex
Notes based on feedback

\subsection{API Design} \label{api_design}
API design is notoriously difficult as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}. Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}. More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}. When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}. One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{shi2011empirical, stylos2006comparing}. The design decisions reached during development of an API will affect the overall usability of the API. Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.

\subsubsection{APIs as Systems}
Motivate why APIs are systems
\cite{761853,5733835}

@@

Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws. The laws are presented in Table \ref{table:expl_laws}. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world. Two other types of systems are also identified; S-type systems and P-type systems. S-type systems are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. An example of a P-type system is a chess program. These types of programs can be derived from a specification, but the rules of the program have to be abstracted. In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.

@@

\subsubsection{APIs as E-Type Systems}
Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes. It is therefore not possible to create an exact specification of any non-trivial API.

@@

>>>>

\subsection{APIs} \label{api_design}
%define what an API is for us
%we consider APIs to be systems because x y z \cite{761853,5733835} 
%Introduce different layers of an API.
%Headers / Interfaces
%Implementation
%"Middle Layer"

\subsubsection{API Design}
API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}. Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}. More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}. When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}. One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{shi2011empirical, stylos2006comparing}. The design decisions reached during development of an API will affect the overall usability of the API. Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.

@@

Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws. The laws are presented in Table \ref{table:expl_laws}. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world. Two other types of systems are also identified; S-type systems and P-type systems. S-type systems are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. An example of a P-type system is a chess program. These types of programs can be derived from a specification, but the rules of the program have to be abstracted. In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible. 
%SPE stuff in here.

@@

@@

\subsubsection{APIs as E-Type Systems}
%Specifics about program type etc here
Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes. It is therefore not possible to create an exact specification of any non-trivial API.
